Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-10-15 talk/pepm2011/paper.tex
minor edit

# inside f: y.is_positive()
guard_class($p_{15}$, BoxedInteger)
    # inside BoxedInteger.is_positive
    $i_{16}$ = get($p_{15}$, intval)
    $i_{17}$ = int_gt($i_{16}$, 0)
# inside f
guard_true($i_{17}$)
jump($p_{15}$, $p_{10}$)
\end{lstlisting}
\caption{Unoptimized Trace for the Simple Object Model}
\label{fig:unopt-trace}
\end{figure}

@@

\begin{itemize}
    \item \lstinline{new} corresponds to object creation.
    \item \lstinline{get} correspond to attribute reads.
    \item \lstinline{set} correspond to attribute writes.
    \item \lstinline{guard_class} correspond to method calls and are followed by
    the trace of the called method.
    \item \lstinline{int_add} and \lstinline{int_get} are integer addition and
    comparison (``greater than''), respectively.
\end{itemize}

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the optimization of partially static data structures
was part of partial evaluation of Prolog programs from the beginning
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again completely disappear in the
residual program, which is equivalent to what our optimization does for an
imperative language.

 FP

partially static data structures: kenichi asai's thesis?

xxx: relation to compile-time garbage collection \cite{mazur_practical_2001};  separation logic; John Hughes: type specialization

>>>>

# inside f: y.is_positive()
guard_class($p_{15}$, BoxedInteger)
    # inside BoxedInteger.is_positive
    $i_{16}$ = get($p_{15}$, intval)
    $i_{17}$ = int_gt($i_{16}$, 0)
# inside f
guard_true($i_{17}$)
jump($p_{15}$, $p_{10}$)
\end{lstlisting}
\caption{An Unoptimized Trace of the Example Interpreter}
\label{fig:unopt-trace}
\end{figure}

@@

\begin{itemize}
    \item \lstinline{new} corresponds to object creation.
    \item \lstinline{get} correspond to attribute reads.
    \item \lstinline{set} correspond to attribute writes.
    \item \lstinline{guard_class} correspond to method calls and are followed by
    the trace of the called method.
    \item \lstinline{int_add} and \lstinline{int_gt} are integer addition and
    comparison (``greater than''), respectively.
\end{itemize}

@@

Partially known data structures are built directly into Prolog (via unbound
logic variables) and thus the treatment of partially static data structures
was part of partial evaluation of Prolog programs from the early stages
\cite{lloyd_partial_1991}. One effect of unfolding in Prolog is that terms that
are constructed and immediately matched again, completely disappear in the
residual program. This is similar to what our optimization does for an
imperative language.

xxx:
partially static data structures: kenichi asai's thesis?

xxx: 
Other related work is compile-time garbage collection \cite{mazur_practical_2001}, which
tries to ....;
  separation logic; John Hughes: type specialization
